---
title: "Distributing Surveys"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Distributing Surveys}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

There is a vast number of distribution related operations you can automate through the Qualtrics API. In this package, 
we provide the following calls:

- `list_distributions`
- `get_distribution`
- `delete_distribution`
- `create_email_distribution`
- `create_reminder_distribution`
- `create_thankyou_distribution`
- `generate_distribution_links`
- `list_distribution_links`
- `send_email_mailinglist`

A number of equivalent calls for sms based distributions are available. Although implemented in the packge, these 
functions are not yet made available to the user due to our inability to perform any kind of testing.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
QualtricsInR::set_qualtrics_opts()
library(QualtricsInR)
```

## Sending your survey through an anonymous link

The first important note to mention is that if you are only looking into distributing your survey through a unique 
public link, you simply need to retrieve the survey id and build the standard URL. For example, if your survey 
id is *SV_abpmKbFCC9hNLzD*, the publically accessible link for thge survey is https://data_center_id.qualtrics.com/jfe/form/SV_abpmKbFCC9hNLzD 
where *data_center_id* can be found in your organisation's identification parameters (see 
[official documentation](https://api.qualtrics.com/v3/docs/api-general-instructions)).

## Scheduling a Qualtrics email distribution

The method described below is a standard approach for people sending their survey to a predefined list of participants through the
Qualtrics emailing service. The use of the API can facilitate the process of managing such distributions for multiple contact lists
with different mailing strategies, for example.

To create a new email distribution, you will need to have created an email body, saved as a Qualtrics library item in your account 
(see functions 'list_messages' and 'create_message'). You will also need the id of the contact list to send the survey to (see 
functions 'list_mailinglists' and 'create_mailinglist').

We show below a step-by-step process to set-up your first email distribution. First, we retrieve the account library id needed
throughout all steps.

```{r}
list_libraries()
```

For a simple user account, you will usually have available the account library and the default Qualtrics library. You've probably
saved your email message in your account library.

You can now list all messages available in the account.

```{r}
list_messages("UR_0NXtl92JJWqfWcJ")
```

We will be using the email *email_for_distribution_test* which we now know the id of. Finally, we need to retrieve the contact list
id for the email recipients.

```{r}
list_mailinglists()
```

We will use the contact list *test_api* we now know the id of. We are now ready to create our email distribution for a given survey.

```{r}
create_email_distribution(
    "SV_erkBAsHrvoJyeYB", # survey id
    "UR_0NXtl92JJWqfWcJ", # library id
    "MS_0fddN2xI3J0nGQZ", # email message id
    "ML_7aoriSKinHh8MfP", # contact list id
    "john.doe@qualtrics.com",  # sender email
    "John Doe", # sender name
    "Participate in this survey",  # email subject
    send_date = paste0(Sys.Date()+1, "T00:00:00Z") # send email tomorrow morning at 00:00
    )
```

This call will return the id of the newly created distribution which allows you to delete the distribution, 
create a reminder distribution or schedule an thank you message.

Note that our Qualtrics account may be set with a different time zone than your local environment. Make sure to specificy 
your date fields accordingly.

There are a number of optional parameters you can find in the function documentation. It is important to note that by the default, 
the sender email will be set to *noreply@qualtrics.com*. You can only use custom email address if your account is appropriately 
configured to do so (see [qualtrics documentation](https://www.qualtrics.com/support/survey-platform/distributions-module/email-distribution/using-a-custom-from-address/))

Note that if you do not want to have to create the email message in Qualtrics before sending the email, the you can use the function
'send_email_mailinglist'.

## Exporting personalized links from Qualtrics

You can also give an instruction for Qualtrics to generate personalized survey links for all contacts of a contact list. You can then
export these links and distribute them through your own organization email service.

```{r}
distribution_id <- generate_distribution_links("SV_erkBAsHrvoJyeYB", "ML_7aoriSKinHh8MfP", "Survey Respondents Generated Links")
print(distribution_id)
list_distribution_links(distribution_id, "SV_erkBAsHrvoJyeYB")
```