---
title: "Distributing Surveys"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Distributing Surveys}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

There is a vast number of distribution related operations you can automate through the Qualtrics API. In this package, we provide the following functions:

- `create_distribution`
- `create_reminder_distribution`
- `create_thankyou_distribution`
- `list_distributions`
- `get_distribution`
- `generate_distributionlink`
- `list_distributionlinks`
- `send_email_tomailinglist`
- `delete_distribution`
- `create_sms_distribution`
- `get_sms_distribution`
- `delete_sms_distribution`
- `list_sms_distributions`


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(QualtricsInR)
```

## Standard use cases

The first important note to mention is that if you are only looking into distributing your survey through a unique public link, you simply need to retrieve the survey id and build the standard URL. For example, if your survey id is *SV_abpmKbFCC9hNLzD*, the publically accessible link for thge survey is https://data_center_id.qualtrics.com/jfe/form/SV_abpmKbFCC9hNLzD where *data_center_id* can be found in your organisation's identification parameters (see [official documentation](https://api.qualtrics.com/v3/docs/api-general-instructions)).

Traditionally, you will send your survey to a predefined list of target respondents for which you create a conact list in Qualtrics. For scheduling such a call through the API

```
# Create a new distribution for a given survey id
dist_id <- create_distribution("")
```
