---
title: "divisions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{divisions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(QualtricsInR)
```

## Create a new division

You can create a new division at the organization level. The only mandatory parameter is the name of the new division. 
You can also pass a list of user ids (see `get_users`) with admin rights for this division. Finally, you can define the 
division permissions, otherwise default permissions will be set.

The call returns the id of the created division.

```r
div_id <- create_division("New_Division", list("UR_1234567890AbCdE"))
```

You can retrieve or update a given division. Since the division permissions are not documented in the API documentation and
do ot always match names of the options seen in the GUI, the time consuming but most reliable appraoch is to retrieve an
existing division and study the json file returned.

```r
div_settings <- get_division("DV_1234567890AbCdE")
```

In the below example, we inactivate the *editSurveyFlow* option for the corresponding division.

```r
options <- list(
   "controlPanel" = list(
     "surveyPermissions" = list(
       "editSurveyFlow" = list("state" = "off"))))
update_division("DV_1234567890AbCdE", permissions = options)
```

In the future, we would like to document the full list of options and provide convenience functions to manipulate these options (see `share_survey`)
