---
title: "divisions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{divisions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(QualtricsInR)
```

## Create a new division

You can create a new division at the organization level. The only mandatory paremeter is the name of the new division. You can also pass a list of 
user ids (see get_users()) with admin rights for this division. Finally, you can define the divisions permissions,
otherwise default permissions will be set. The call returns the id of the created division.

```
div_id <- create_division("New_Division", list("UR_1234567890AbCdE"))
```

You can retrieve or update a given division. The best way to figure out the permissions you have accessible for the first call
is to retrieve an exisiting division from Qualtrics and study the json reply below.

```
json_rep <- get_division("DV_1234567890AbCdE")
update_division("DV_1234567890AbCdE", name = "New_Name")
```
