---
title: "Survey Reponses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Survey Reponses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(QualtricsInR)
set_qualtrics_opts(Sys.getenv("QUALTRICSINR_TEST_TOKEN"))
```

In addition of providing a standard method for exporting the responses of a survey, 
[QualtricsInR](https://github.com/ppssphysics/QualtricsInR) provides an useful method for 
efficiently handling the download of multiple surveys.

The process to retrieve survey data requires 3 steps: 1) request the data from Qualtrics, 2) wait while the data 
is being prepared, 3) download the data (more information can be found 
[here](https://api.qualtrics.com/docs/getting-survey-responses-new)). It may therefore be more efficient, when 
downloading responses from multiple surveys to 1) request the downloads 2) download the prepared files once they are ready.

## Finding your Survey Id

You can always find the id of one of your surveys by logging into your Qualtrics account and inspecting the URL when 
previewing your survey or inspect your Qualtrics IDs account page. Through the API, it is however straightforward to list all
the surveys available in your account:

```{r}
# retrieve all available survey ids from your account
lst_surveys <- list_surveys()
print(lst_surveys)
```

## Survey Response Status

Rather than exporting the full set of responses from a survey, you might only be interested in checking the current status of total responses:

```{r}
get_survey_response_counts("SV_elpspu2EuJXLEWx")
```

The call returns a list with 3 elements corresponding to the valid survey responses ('auditable'), the responses that were
generated or deleted.

## Standard Export Method

You can export the responses from your survey using the `get_survey_responses()` function. To retrieve the id of your
survey, you can use the `list_surveys` function.

```{r}
# export survey responses
get_survey_responses("SV_cScDRSV5hsN3YEd")
```

By default, the data is not saved on disk. You can save your data in a desired location by using the *saveDir* argument.

```
get_survey_responses("SV_cScDRSV5hsN3YEd", format = "csv", saveDir = "./data/", filename = "test_survey")
```

The default file format is json but csv and tsv can be passed. We currently don't provide the SPSS file 
format as an output option. The file is automatically named with the survey id if the parameter *filename* is not
specified.

A number of [optional parameters](https://api.qualtrics.com/api-reference/reference/responseImportsExports.json/paths/~1surveys~1%7BsurveyId%7D~1export-responses/post) can be passed 
to the function. Be aware that any download that exceeds 1.8 GB will need to be split in several exports 
using different time intervals (dates specifications follow the ISO 8601 standard YYYY-MM-DD 
(more information [here](https://api.qualtrics.com/docs/dates-and-times)). For example:

```
get_survey_responses(
  "SV_cScDRSV5hsN3YEd", 
  format = "csv", 
  startDate = "2020-04-01T07:31:43Z", 
  endDate = "2020-04-29T07:31:43Z")
```

Instead of exporting the recode value for the answer choices, you can export the text of the answer choice by setting the
parameter *useLabels* to TRUE:

```
get_survey_responses(
  "SV_cScDRSV5hsN3YEd", 
  format = "csv", 
  useLabels = TRUE)
```

## Retrieving Responses for Multiple Surveys

If you need to download responses from multiple surveys or you have a need to schedule regular automated exports 
of multiple survey responses, we recommend you use the approach documented below. Instead of looping over each 
survey, requesting the export and downloading the file from the Qualtrics server, we will send the request to Qualtrics
to prepare all the files and then export them.

```{r}
# request creation of response exports
requests <- request_downloads(lst_surveys$id, format = "csv")
requests
# download the response files
data <- download_requested(requests)
length(data)
head(data[[1]])
```

The download will return a list with each element containing the responses for each individual survey.

The implementation takes into account the rate limit imposed by Qualtrics for this specific call. Once the limit 
is attained in looping accross the different survey ids, the procedure waits a few seconds before trying again. 
You can set the parameter *retryOnRateLimit* to FALSE and the procedure will stop upon the first error returned 
by Qualtrics.

## Downloading Responses In Progress

One useful functionality is the ability to retrieve a survey's in progress responses.

```
# for one specific survey
get_survey_responses(survids$id[16], format = "csv", exportResponsesInProgress = TRUE)
# looping on multiple survey ids
request_downloads(survids$id[1:5], format = "csv", exportResponsesInProgress = TRUE)
```