---
title: "Survey Objects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Survey Objects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(QualtricsInR)
QualtricsInR::set_qualtrics_opts()
```

Manipulating survey flows through the API can be useful but applies only to very
specific use cases. An example is building through the Qualtrics UI a survey template 
that will need to be duplicated multiple times, each time with slight updates to 
the flow of questions, blocks, etc.

Moreover, using the flow related functions are not straightforward and will require 
additional work to understand the basics and indepensables of a flow structure and 
how modifying the flow impacts other key strcutural elements.

There are 3 main functions to intereact with survey flows:

* `get_survey_flow` retrieves a survey's flow as a nested list
* `update_survey_flow` allows to update the complete survey object (removing or adding elements)
* `update_flow_element` update the details of a specific survey flow element.

As a simple example, we retrieve below the flow for a 2 questions survey, split into 2 blocks.

```{r}
flow <- get_survey_flow("SV_5haBIVgvUtsvQ1v")
names(flow)
```

The list contains 4 elements which define the key properties of a flow element. 

Flow is the elements that contains the whole flow structure. Here we have 2 seb-elements
corresponding to our 2 blocks in the survey:

```{r}
length(flow$Flow)
```

Properties contain at mimimum the Count variable that tell how many elements make up the flow. 
Remember the top-level Flow element returned in the list counts as an element so the count here is
3 (2 blocks and 1 top level flow element).

```{r}
flow$Properties$Count
```

FlowID is a unique id for the flow element (written as "FL_")

```{r}
c(flow$FlowID, flow$Flow[[1]]$FlowID, flow$Flow[[2]]$FlowID)
```

Type defines different possible type of flow elements. For this survey, we find:
```{r}
c(flow$Type, flow$Flow[[1]]$Type, flow$Flow[[2]]$Type)
```

Each children flow element can have a specific ID that links that flow element to a
specific object of the survey, for instance, here, block Ids.

Looking at updating the flow, we could for example switch the order of the two flow elements. To, we
just invert the list order as well as the flow ids to match the new order.


```{r}
flow_1 <- flow$Flow[[2]]
flow_2 <- flow$Flow[[1]]
flow_1$FlowID <- flow$Flow[[1]]$FlowID
flow_2$FlowID <- flow$Flow[[2]]$FlowID
flow_1$ID <- flow$Flow[[1]]$ID
flow_2$ID <- flow$Flow[[2]]$ID
flow$Flow[[1]] <- flow_1
flow$Flow[[2]] <- flow_2
```

Sending the updated flow request requires to decouple the flow object in its different elements:

```{r}
update_survey_flow(
  "SV_5haBIVgvUtsvQ1v", 
  as.character(flow$FlowID), 
  as.character(flow$Type),
  flow$Flow,
  flow$Properties)
```

