---
title: "Surveys"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Surveys}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
QualtricsInR::set_qualtrics_opts()
library(QualtricsInR)
```

## Survey Manipulation

Using the Qualtrics API, you can peform a number of manipulations of survey objects in your Qualtrics account:

- [Simple survey manipulation](#Simple survey manipulation)
- [Copying and sharing surveys](#Copying and sharing surveys)
- [Importing a survey](#Importing a survey)

### Simple survey manipulation

You can easily retrieve the full list of surveys available in your account:

```{r}
surveys <- list_surveys()
head(surveys)
```

Using a survey id, you can retrieve the survey object from your account:

```{r}
srv_obj <- get_survey(surveys$id[1])
```

The call returns a list that provides a number of information related to the status of the survey, providing a quick and efficient way 
to see the number of survey responses for example, instead of going through the more time consuming process of exporting all survey
responses through `get_survey_responses`.

```{r}
names(srv_obj$result)
```

A small number of survey options can be easily updated through the below. These include: the survey name, the activity status,
the time range and the owner id.

```r
# set status to active
update_survey(surveys$id[1], status = TRUE)
# set time range
update_survey(surveys$id[1], expiration = c("2016-01-01T01:00:00Z","2016-03-01T01:00:00Z"))
```

Although not a complete overlap, the `update_options` provide many more survey global options (see below).

### Copying and sharing surveys

You can create a copy of a survey in your own account or in another users account using the user if (see `get_users`):

``` r
# Copy a survey in your own account
copy_survey(survey_id, "New_Copy")
# Copy a survey to another user's account
copy_survey(survey_id, "New_Copy",user_id)
```

The survey id of the new copy will be returned.

You might not want to copy a survey into another person's account but would rather share the project defining a specific set
of permissions. By default, without any specification, your project will be shared with all permissions disabled. 
You can decide which permissions to enable by providing an array of numbers indicating the permissions you want to enable. 

The available options are listed below:

``` r
"1"="copySurveyQuestions"
"2"="editSurveyFlow"
"3"="useBlocks"
"4"="useSkipLogic"
"5"="useConjoint"
"6"="useTriggers"
"7"="useQuotas"
"8"="setSurveyOptions"
"9"="editQuestions"
"10"="deleteSurveyQuestions"
"11"="editSurveys"
"12"="activateSurveys"
"13"="deactivateSurveys"
"14"="copySurveys"
"15"="distributeSurveys"
"16"="deleteSurveys"
"17"="translateSurveys"
"18"="editSurveyResponses"
"19"="createResponseSets"
"20"="viewResponseId"
"21"="useCrossTabs"
"22"="downloadSurveyResults"
"23"="viewSurveyResults"
"24"="filterSurveyResults"
"25"="viewPersonalData"
```

As an example, to share the survey with only distribution rights enabled, you run the following call:

``` r
share_survey(my_surveys[1], user_id, 15)
```

Previous calls are overridden by any new permissions setting so you must set every permission each time. To add permissions to visualize the data, do:

``` r
# enable permissions for distribution and data visualisation
share_survey(my_surveys[1], user_id, c(15,23))
# remove permission to visualize the data
share_survey(my_surveys[1], user_id, c(15))
```

### Importing a survey

You can import a local survey file into Qualtrics. The accepted file formats are *qsf*, *txt* and *doc* (word document). The *qsf* format stands for *qualtrics survey file* and is usually a file exported from Qualtrics. This is however nothing else than json that is not impossible to build from scratch (be ready to sweat though).

The file can be imported from a local path or directly from a url:

```r
# Import a local qsf file into Qualtrics
import_survey("name", "./survey.qsf", 1)
# Import a file from a url
import_survey("name", "https://www.example.com/mysurvey.qsf", 1)
```

## Manipulating Survey Objects

The Qualtrics API provides a number of functionalities to interact directly with a survey's internal structure. There is the possiblity to intereact with:

* Questions
* Flows
* Blocks
* Survey Options

### Flows

Although not part of the flow adminstration itself, a useful relation function allows to insert embedded data fields in your survey `insert_embedded_data`.


### Survey Options

A exhaustive list of survey options are configurable through the `update_options` call.

```r
update_options(surveys$id[1], list("BackButton" = true, "BallotBoxStuffingPrevention" = true))
```

All available options can be found in the [documention](https://api.qualtrics.com/reference#update-options).
