---
title: "Basic survey manipulations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic survey manipulations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(QualtricsInR)
set_qualtrics_opts(Sys.getenv("QUALTRICSINR_TEST_TOKEN"))
```

Using the Qualtrics API, you can peform a number of manipulations of survey objects in your Qualtrics account.

You can easily retrieve the full list of surveys available in your account:

```{r}
surveys <- list_surveys()
head(surveys)
```

Using a survey id, you can retrieve the survey object from your account:

```{r}
srv_obj <- get_survey(surveys$id[1])
```

The call returns a list that provides a number of information related to the status of the survey, providing a quick and efficient way 
to see the number of survey responses for example, instead of going through the more time consuming process of exporting all survey
responses through `get_survey_responses()`.

```{r}
names(srv_obj)
```

A small number of survey options can be easily updated through the below. These include: the survey name, the activity status,
the time range and the owner id.

```r
# set status to active
update_survey(surveys$id[1], status = TRUE)
# set time range
update_survey(surveys$id[1], expiration = c("2016-01-01T01:00:00Z","2016-03-01T01:00:00Z"))
```

An exhaustive list of survey options are configurable through the `update_options()` call.

```r
update_options(surveys$id[1], list("BackButton" = true, "BallotBoxStuffingPrevention" = true))
```

All available options can be found in the [documention](https://api.qualtrics.com/reference#update-options).

## Copying and sharing surveys

You can create a copy of a survey in your own account or in another user's account using the user id (if you are a brand administrator, see `list_users()`):

``` r
# Copy a survey in your own account
copy_survey(survey_id, "New_Copy")
# Copy a survey to another user's account
copy_survey(survey_id, "New_Copy", user_id)
```

The survey id of the new copy will be returned.

You might not want to copy a survey into another person's account but would rather share the project defining a specific set
of permissions. By default, without any specification, your project will be shared with all permissions disabled.  You can decide which 
permissions to enable by providing an array of numbers indicating the permissions you want to enable. 

The available options are listed below:

``` r
"1"="copySurveyQuestions"
"2"="editSurveyFlow"
"3"="useBlocks"
"4"="useSkipLogic"
"5"="useConjoint"
"6"="useTriggers"
"7"="useQuotas"
"8"="setSurveyOptions"
"9"="editQuestions"
"10"="deleteSurveyQuestions"
"11"="editSurveys"
"12"="activateSurveys"
"13"="deactivateSurveys"
"14"="copySurveys"
"15"="distributeSurveys"
"16"="deleteSurveys"
"17"="translateSurveys"
"18"="editSurveyResponses"
"19"="createResponseSets"
"20"="viewResponseId"
"21"="useCrossTabs"
"22"="downloadSurveyResults"
"23"="viewSurveyResults"
"24"="filterSurveyResults"
"25"="viewPersonalData"
```

As an example, to share the survey with only distribution rights enabled, you run the following call:

``` r
share_survey(my_surveys[1], user_id, 15)
```

Previous calls are overridden by any new permissions setting so you must set every permission each time. To add permissions to visualize the data, do:

``` r
# enable permissions for distribution and data visualisation
share_survey(my_surveys[1], user_id, c(15,23))
# remove permission to visualize the data
share_survey(my_surveys[1], user_id, c(15))
```

## Importing a survey

You can import a local survey file into Qualtrics. The accepted file formats are *qsf*, *txt* and *doc* (word document). The *qsf* format 
stands for *qualtrics survey file* and is usually a file exported from Qualtrics. This is however nothing else than json that is not 
impossible to build from scratch (be ready to sweat though).

The file can be imported from a local path or directly from a url:

```r
# Import a local qsf file into Qualtrics
import_survey("name", "./survey.qsf", 1)
# Import a file from a url
import_survey("name", "https://www.example.com/mysurvey.qsf", 1)
```

## Languages and Translations

You can check the languages currently enabled for the survey with `get_survey_languages`. You 
can update available languages, for example adding Spanish and Portuguese to the base english
survey:

```r
update_survey_languages("SV_1873930DS2", c("EN", "ES", "PT"))
```

You can retrieve a given translation, which will return a list of all survey textual items that can
be translated.

```r
srv_transl_pt <- get_survey_translations("SV_1873930DS2", "PT")
```

This can be useful if you want to handle your translation process outide of Qualtrics. Provide you keep the
item references and struture of the list untouched, you will thn be able to update the survey translation back
into Qualtrics:

```r
update_survey_translations(id, "PT", srv_transl_pt)
```

Another compelling use case is to export different languages from multiple clones of a
survey and import it back into the master version.

## Manipulating Survey Objects

The Qualtrics API provides a number of functionalities to interact directly with a survey's internal structure. There is the possiblity to intereact with:

* Questions
* Flows
* Blocks
* Survey Options


