---
title: "Survey Reponses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Survey Reponses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
QualtricsInR::set_qualtrics_opts()
library(QualtricsInR)
```

In addition of providing a standard method for exporting the responses of a survey, [QualtricsInR](https://github.com/ppssphysics/QualtricsInR) provides an useful method for efficiently handling the download of multiple surveys.

The process to retrieve survey data requires 3 steps: 1) request the data from Qualtrics, 2) wait while the data is being prepared, 3) download the data (more information can be found [here](https://api.qualtrics.com/docs/getting-survey-responses-new)). It may therefore be more efficient, when downloading responses from multiple surveys to 1) request the downloads 2) download the prepared files once they are ready.

## Standard Export Method

You can export the responses from your survey using the `get_survey_responses` function.

```{r}
# retrieve all survey ids from your account
survids <- list_surveys()
head(survids)
# export survey responses, returned ads a list of all surveys' results
dt <- get_survey_responses(survids$id[16], format = "csv")
head(dt)
```

The default file format is json but csv and tsv can be passed. We currently don't provide the SPSS file format as an output option.

A number of [optional parameters](https://api.qualtrics.com/docs/getting-survey-responses-new) can be passed to the function. Be aware that any download that exceeds 1.8 GB will need to be split in several exports using different time intervals (dates specifications follow the ISO 8601 standard YYYY-MM-DD (more information [here](https://api.qualtrics.com/docs/dates-and-times)).

```r
# export survey and save it the local folder
get_survey_responses(survids$id[16], format = "csv", saveDir = "./")
# ask an export for all responses after April 1st, 2016 and before April 25 2016
start <- "2016-04-01T07:31:43Z"
end <- "2016-04-25T07:31:43Z"
get_survey_responses(survids$id[16], format = "csv", startDate = start, endDate = end)
```

By default, Qualtrics will now set the *useLabels* option to FALSE, which exports question results as the recode values of the answer choices. If you want instead to export the text of the answer choice, set the value to TRUE.

## Retrieving Multiple Surveys

If you need to download responses from multiple surveys or you have a need to schedule regular automated exports of multiple survey responses, we recommend you use the approach described below:

```{r}
requests <- request_downloads(survids$id[1:5], format = "csv")
requests
# download the data
data <- download_requested(requests)
length(data)
```

The implementation takes into account the rate limit imposed by Qualtrics for this specific call. Once the limit is attained in looping accross the different survey ids, the procedure waits a few seconds before trying again. You can set the paramter *retryOnRateLimit* to FALSE and the procedure will stop upon the first error returned by Qualtrics.

### Download Responses In Progress

One useful parameter that was recently added by Qualtrics is the ability to retrieve a survey's *in progress* responses.

```r
dt <- get_survey_responses(survids$id[16], format = "csv", exportResponsesInProgress = TRUE)
```
